Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-20 chapters/paper3.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion

In this chapter, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, focusing on the influence of initial microstructure and the 
application of a constant magnetic field on their shear response. The shear behavior was characterized using a Herschel-Bulkley fitting function to extract the flow index, 
consistency index, and yield stress. My analysis confirmed that the shear-thinning nature of bijels remains robust, regardless of particle morphology or applied magnetic 
field. However, the flow index and yield stress trends were strongly dependent on these factors.  
I found that increased particle ordering led to distinct yield stress behaviors: oblate particles resulted in a lower yield stress, while prolate particles exhibited a 
higher yield stress. When examining the properties of the particle monolayer, I identified a clear impact of particle morphology on interparticle interactions at the 
interface. In the absence of a magnetic field, both particle monolayers remained adsorbed at the interface. However, when a magnetic field was initially applied, the 
behavior diverged significantly oblate particles flipped out of the interface to minimize interfacial energy, whereas prolate particles tilted out. These differences 
directly influenced the shear response, altering how the surrounding fluid flows around the particles and leading to the observed non-Newtonian behavior and yield 
stress characteristics.  
Furthermore, I investigated the microstructural effects of shear and magnetic field-induced particle ordering and found that coarsening was the primary driver of 
domain size evolution in sheared bijels. This coarsening was facilitated by a reduction in interfacial particle coverage. When analyzing the anisotropic domain size evolution, 
I observed that in most cases, the direction of greatest structural change aligned with expected trends—except when the magnetic field was switched off. This deviation is 
attributed to differences in particle monolayer evolution, depending on whether the bijel was formed with or without an initially applied field.

@@

>>>>

@@

\section{Conclusions}

% In this chapter, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, focusing on the influence of initial microstructure and the 
% application of a constant magnetic field on their shear response. The shear behavior was characterized using a Herschel-Bulkley fitting function to extract the flow index, 
% consistency index, and yield stress. My analysis confirmed that the shear-thinning nature of bijels remains robust, regardless of particle morphology or applied magnetic 
% field. However, the flow index and yield stress trends were strongly dependent on these factors.  
% I found that increased particle ordering led to distinct yield stress behaviors: oblate particles resulted in a lower yield stress, while prolate particles exhibited a 
% higher yield stress. When examining the properties of the particle monolayer, I identified a clear impact of particle morphology on interparticle interactions at the 
% interface. In the absence of a magnetic field, both particle monolayers remained adsorbed at the interface. However, when a magnetic field was initially applied, the 
% behavior diverged significantly oblate particles flipped out of the interface to minimize interfacial energy, whereas prolate particles tilted out. These differences 
% directly influenced the shear response, altering how the surrounding fluid flows around the particles and leading to the observed non-Newtonian behavior and yield 
% stress characteristics.  
% Furthermore, I investigated the microstructural effects of shear and magnetic field-induced particle ordering and found that coarsening was the primary driver of 
% domain size evolution in sheared bijels. This coarsening was facilitated by a reduction in interfacial particle coverage. When analyzing the anisotropic domain size evolution, 
% I observed that in most cases, the direction of greatest structural change aligned with expected trends—except when the magnetic field was switched off. This deviation is 
% attributed to differences in particle monolayer evolution, depending on whether the bijel was formed with or without an initially applied field.

The rheological properties of bijels are of importance in many fabrication schemes such as STrIPS and homogenization. \cite{haase_continuous_2015,cai_bijels_2017}
To characterize how magnetically responsive bijels can be used in these synthesis techniques, I studied the effect of particle morphology, initial microstructure and
applied magnetic fields on the rheology of bijels experiencing a constant shear. Bijel templates made with $\bar{B} = 0$ and $\bar{B} = 1$ were selected, with field strengths
of $\bar{B} = 0$ and $\bar{B} = 1$ applied to each template. This results in four processing histories per particle morphology namely $\bar{B}:0 \rightarrow 0$,
$\bar{B}:0 \rightarrow 1$, $\bar{B}:1 \rightarrow 0$ and $\bar{B}:1 \rightarrow 1$. I then apply a constant shear rate onto each bijel.

I first characterized the shear stress imparted by bijels under several strain rates. The shear stress calculated continued to increase in line with expectations
for colloidal glasses as ageing occurs. Thus a pseudo-steady state was selected to compare the shear properties of the bijel.
I fit the shear stress data using a Herschel Buckley fit and identify that the flow index of bijels stabilized by ellipsoidal 
particles under magnetic fields became less shear thinning. The yield stress of bijels stabilized by oblate particles was shown to reduce by 4x while the yield stress
of bijels stabilized by prolate particles was shown to increase by 2x upon application of magnetic fields.

To characterize these differences, closer attention is paid to the particle monolayer of the bijel. Shear induced reorientation of the ellipsoids can be observed in cases
where a magnetic field was used observed, characterized as the orientation of particles drift away from the magnetic field direction. When analyzing the effect this reorientation
has on the particles at the interface, the interface angle in all cases increases as a function of the shear rate. However the quantitative behavior of oblate particles differ
from prolate particles. Under magnetic fields, oblate particles tend to flip out of the interface while prolate particles tilt out of the interface. The impact that
the particle tilting and flipping out of the interface can also be seen in the number of particles in the interface, where the differences in the particle morphology 
can be characterized as differences in the number of particles at the interface in response to the magnetic field.

A reduction in the number of particles at the interface and the particles tilting out of the interface reduces the interfacial coverage. The reduction in interfacial
coverage manifests as domain coarsening, characterized as a smooth decrease in the magnitude of the area averaged Gaussian curvature. The changes in the particle monolayer
properties manifest as changes in the evolution of the directional domain size evolution due to shear induced particle reorientation at the interface.

Past literature
has shown how bijels are susceptible to failure when being used as crossflow reactors due to shear induced domain coarsening resulting in microstructure failure. 
\cite{boakye-ansah_controlling_2020} The investigations conducted here demonstrate that controlling the orientations of particles at interfaces are crucial to 
the rheological properties of bijels. Other properties not considered here such as different particle aspect ratios, the effect of surface tension on the shear response of
bijels and the volume fraction of particles are not considered here. Additionally, complex rheology of the bijels can determine detailed rheological properties such as the
gel point and phase difference of the bijel which can yield further rheological characterization of bijels stabilized by magnetically responsive ellipsoidal particles.
